Dm General Read Sequence Figure Generation

### 2022-05-31 R/DrosophilaDeaminationSequenceAndPositionFigureGeneration.rmd
Created drosophila notebooks

---
title: "NHF1 Deamination Sequence and Position Figure Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
  filtering:
    label: "Filtering"
    value: NONE
    input: select
    choices: [NONE, TGG_filtered]
---

@@

cellType = "NHF1"
CPDTimepoints = list(`1h` = NULL, `8h` = NULL, `24h` = NULL, `48h` = NULL)
sixFourTimepoints = list(`5min` = NULL, `20min` = NULL, `1h` = NULL)
minReadLength = 22; maxReadLength = 30

@@

```{r read_simplified_mismatch_data}
# Get file paths for the mismatch by read data
CPDMismatchData = list(rep1 = CPDTimepoints,
                       rep2 = CPDTimepoints)
for (i in seq_along(CPDMismatchData)) {
  for (j in seq_along(CPDMismatchData[[i]])) {
    CPDMismatchData[[i]][[j]] = fread(generateFilePath(
      deaminationSequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
      cellType = cellType, lesion = "CPD", timepoint = names(CPDMismatchData[[i]])[j],
      repitition = names(CPDMismatchData)[i], filtering = filtering
    ))
  }
}

sixFourMismatchData = list(rep1 = sixFourTimepoints,
                           rep2 = sixFourTimepoints)
for (i in seq_along(sixFourMismatchData)) {
  for (j in seq_along(sixFourMismatchData[[i]])) {
    sixFourMismatchData[[i]][[j]] = fread(generateFilePath(
      deaminationSequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
      cellType = cellType, lesion = "6-4", timepoint = names(sixFourMismatchData[[i]])[j],
      repitition = names(sixFourMismatchData)[i], filtering = filtering
    ))
  }
}
```

@@

```{r 6-4_mismatch_type_frequency}
for (i in 1:length(sixFourMismatchData)) {
  for (j in 1:length(sixFourMismatchData[[i]])) {
    plotMismatchTypeFrequencies(sixFourMismatchData[[i]][[j]],
                                title = paste(c("6-4", titleCaseFiltering, names(sixFourMismatchData)[i], 
                                                names(sixFourMismatchData[[i]])[j], "Mismatch Type Frequency"),
                                              collapse = ' '))
  }
}
```

@@

```{r 6-4_mismatch_pos_frequency}
for (i in 1:length(sixFourMismatchData)) {
  for (j in 1:length(sixFourMismatchData[[i]])) {
    plotMismatchPositionFrequencies(sixFourMismatchData[[i]][[j]], includedTypes = c("C>T"),
                                    title = paste(c("6-4", titleCaseFiltering, names(sixFourMismatchData)[i], 
                                                    names(sixFourMismatchData[[i]])[j], "C>T Mismatch Positions"),
                                                  collapse = ' '))
    plotMismatchPositionFrequencies(sixFourMismatchData[[i]][[j]], omittedTypes = c("C>T"),
                                    title = paste(c("6-4", titleCaseFiltering, names(sixFourMismatchData)[i], 
                                                    names(sixFourMismatchData[[i]])[j], "!C>T Mismatch Positions"),
                                                  collapse = ' '))
  }
}
```

@@

```{r 6-4_trinucleotide_context_analysis}
for (i in 1:length(sixFourMismatchData)) {
  for (j in 1:length(sixFourMismatchData[[i]])) {
    plotTrinucleotideContext(sixFourMismatchData[[i]][[j]], includedTypes = c("C>T"),
                             title = paste(c("6-4", titleCaseFiltering, names(sixFourMismatchData)[i],
                                             names(sixFourMismatchData[[i]])[j], "C>T Mismatch Trinuc Context"),
                                           collapse = ' '))
  }
}
```

```{r read_mismatch_frequency_z-score_tables}
CPDMMFreqZScores = list(rep1 = CPDTimepoints, rep2 = CPDTimepoints)
for (i in seq_along(CPDMMFreqZScores)) {
  for (j in seq_along(CPDMMFreqZScores[[i]])) {
    CPDMMFreqZScores[[i]][[j]] = fread(generateFilePath(
      directory = deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
      cellType = cellType, lesion = "CPD", repitition = names(CPDMMFreqZScores)[i],
      timepoint = names(CPDMMFreqZScores[[i]])[j], filtering = filtering, includedMismatches = c("C>T")
    ))
  }
}

sixFourMMFreqZScores = list(rep1 = sixFourTimepoints, rep2 = sixFourTimepoints)
for (i in seq_along(sixFourMMFreqZScores)) {
  for (j in seq_along(sixFourMMFreqZScores[[i]])) {
    sixFourMMFreqZScores[[i]][[j]] = fread(generateFilePath(
      directory = deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
      cellType = cellType, lesion = "6-4", repitition = names(sixFourMMFreqZScores)[i],
      timepoint = names(sixFourMMFreqZScores[[i]])[j], filtering = filtering, includedMismatches = c("C>T")
    ))
  }
}
```

@@

```{r 6-4_mismatch_position_frequencies_by_read_length, fig.width = 9, fig.height = 5}
plotPositionAcrossTimepointAndReadLength(sixFourMismatchData$rep1, includedTypes = c("C>T"),
                                         title = paste(c("6-4", titleCaseFiltering, "C>T Mismatch Pos Freq Rep1"),
                                                       collapse = ' '),
                                         zScoreTables = sixFourMMFreqZScores$rep1)
plotPositionAcrossTimepointAndReadLength(sixFourMismatchData$rep2, includedTypes = c("C>T"),
                                         title = paste(c("6-4", titleCaseFiltering, "C>T Mismatch Pos Freq Rep2"),
                                                       collapse = ' '),
                                         zScoreTables = sixFourMMFreqZScores$rep2)
plotPositionAcrossTimepointAndReadLength(sixFourMismatchData$rep1, includedTypes = c("C>T"), posType = FIVE_PRIME,
                                         title = paste(c("6-4", titleCaseFiltering, "C>T Mismatch Pos Freq Rep1"),
                                                       collapse = ' '),
                                         zScoreTables = sixFourMMFreqZScores$rep1)
plotPositionAcrossTimepointAndReadLength(sixFourMismatchData$rep2, includedTypes = c("C>T"), posType = FIVE_PRIME,
                                         title = paste(c("6-4", titleCaseFiltering, "C>T Mismatch Pos Freq Rep2"),
                                                       collapse = ' '),
                                         zScoreTables = sixFourMMFreqZScores$rep2)
```

@@

```{r 6-4_read_length_distributions}
plotReadLengthFrequencies(sixFourMismatchData$rep1,
                          title = paste(c("6-4", titleCaseFiltering, "Read Length Freq Rep 1"), collapse = ' '))
plotReadLengthFrequencies(sixFourMismatchData$rep2,
                          title = paste(c("6-4", titleCaseFiltering, "Read Length Freq Rep 2"), collapse = ' '))
```

```{r read_mismatch_position_statistics}
CPDGroupedStats = list(rep1 = list(three_prime = NULL, five_prime = NULL),
                       rep2 = list(three_prime = NULL, five_prime = NULL))
for (i in seq_along(CPDGroupedStats)) {
  for (j in seq_along(CPDGroupedStats[[i]])) {
    CPDGroupedStats[[i]][[j]] = fread(generateFilePath(
      deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
      cellType = cellType, lesion = "CPD", repitition = names(CPDGroupedStats)[i],
      strandPolarity = names(CPDGroupedStats[[i]])[j], filtering = filtering
    ))
  }
}

sixFourGroupedStats = list(rep1 = list(three_prime = NULL, five_prime = NULL),
                           rep2 = list(three_prime = NULL, five_prime = NULL))
for (i in seq_along(sixFourGroupedStats)) {
  for (j in seq_along(sixFourGroupedStats[[i]])) {
    sixFourGroupedStats[[i]][[j]] = fread(generateFilePath(
      deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
      cellType = cellType, lesion = "6-4", repitition = names(sixFourGroupedStats)[i],
      strandPolarity = names(sixFourGroupedStats[[i]])[j], filtering = filtering
    ))
  }
}
```

@@

```{r 6-4_position_differences_across_read_lengths, fig.width = 9, fig.height = 5}
plotGroupedPositionStats(sixFourGroupedStats$rep1$three_prime, sixFourGroupedStats$rep1$five_prime, POS_DIFF,
                         title = paste(c("6-4", titleCaseFiltering, "C>T Mismatch Pos Diff Rep1"), collapse = ' '),
                         xAxisBreaks = c(minReadLength:maxReadLength))
plotGroupedPositionStats(sixFourGroupedStats$rep2$three_prime, sixFourGroupedStats$rep2$five_prime, POS_DIFF,
                         title = paste(c("6-4", titleCaseFiltering, "C>T Mismatch Pos Diff Rep2"), collapse = ' '),
                         xAxisBreaks = c(minReadLength:maxReadLength))
```

>>>>

---
title: "Dm Deamination Sequence and Position Figure Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
  filtering:
    label: "Filtering"
    value: NONE
    input: select
    choices: [NONE, TGG_filtered]
---

@@

cellType = "Dm"
CPDTimepoints = list(`10m` = NULL, `30m` = NULL, `8h` = NULL, `16h` = NULL, `24h` = NULL)
minReadLength = 23; maxReadLength = 32

@@

```{r read_simplified_mismatch_data}
# Get file paths for the mismatch by read data
CPDMismatchData = list(rep1 = CPDTimepoints,
                       rep2 = CPDTimepoints)
for (i in seq_along(CPDMismatchData)) {
  for (j in seq_along(CPDMismatchData[[i]])) {
    CPDMismatchData[[i]][[j]] = fread(generateFilePath(
      deaminationSequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
      cellType = cellType, lesion = "CPD", timepoint = names(CPDMismatchData[[i]])[j],
      repitition = names(CPDMismatchData)[i], filtering = filtering
    ))
  }
}
```

@@

@@

@@

```{r read_mismatch_frequency_z-score_tables}
CPDMMFreqZScores = list(rep1 = CPDTimepoints, rep2 = CPDTimepoints)
for (i in seq_along(CPDMMFreqZScores)) {
  for (j in seq_along(CPDMMFreqZScores[[i]])) {
    CPDMMFreqZScores[[i]][[j]] = fread(generateFilePath(
      directory = deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
      cellType = cellType, lesion = "CPD", repitition = names(CPDMMFreqZScores)[i],
      timepoint = names(CPDMMFreqZScores[[i]])[j], filtering = filtering, includedMismatches = c("C>T")
    ))
  }
}
```

@@

@@

```{r read_mismatch_position_statistics}
CPDGroupedStats = list(rep1 = list(three_prime = NULL, five_prime = NULL),
                       rep2 = list(three_prime = NULL, five_prime = NULL))
for (i in seq_along(CPDGroupedStats)) {
  for (j in seq_along(CPDGroupedStats[[i]])) {
    CPDGroupedStats[[i]][[j]] = fread(generateFilePath(
      deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
      cellType = cellType, lesion = "CPD", repitition = names(CPDGroupedStats)[i],
      strandPolarity = names(CPDGroupedStats[[i]])[j], filtering = filtering
    ))
  }
}
```

@@

### 2022-05-31 R/DrosophilaGeneralReadSequenceDataGeneration.rmd
Created drosophila notebooks

---
title: "NHF1 General Read Sequence Data Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
---

@@

```{r compute_and_write_6-4_sequence_frequency}
for (repitition in c("rep1", "rep2")) {
  for (timepoint in names(sixFourTimepoints)) {
    singleFileFullAnalysis("6-4", repitition, timepoint)
  }
}
```

>>>>

---
title: "Dm General Read Sequence Data Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
---

@@

### 2022-05-31 R/DrosophilaGeneralReadSequenceFigureGeneration.rmd
Created drosophila notebooks

---
title: "NHF1 General Read Sequence Figure Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
---

@@

CPDCGASeqFreq = list(rep1 = CPDTimepoints, rep2 = CPDTimepoints)
for (i in seq_along(CPDCGASeqFreq)) {
  for (j in seq_along(CPDCGASeqFreq[[i]])) {
    CPDCGASeqFreq[[i]][[j]] = fread(generateFilePath(
      directory = generalReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
      cellType = cellType, lesion = "CPD", repitition = names(CPDCGASeqFreq)[i],
      timepoint = names(CPDCGASeqFreq[[i]])[j], sequence = "CGA"
    ))
  }
}

sixFourTGGSeqFreq = list(rep1 = sixFourTimepoints, rep2 = sixFourTimepoints)
for (i in seq_along(sixFourTGGSeqFreq)) {
  for (j in seq_along(sixFourTGGSeqFreq[[i]])) {
    sixFourTGGSeqFreq[[i]][[j]] = fread(generateFilePath(
      directory = generalReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
      cellType = cellType, lesion = "6-4", repitition = names(sixFourTGGSeqFreq)[i],
      timepoint = names(sixFourTGGSeqFreq[[i]])[j], sequence = "TGG"
    ))
  }
}

sixFourCGASeqFreq = list(rep1 = sixFourTimepoints, rep2 = sixFourTimepoints)
for (i in seq_along(sixFourCGASeqFreq)) {
  for (j in seq_along(sixFourCGASeqFreq[[i]])) {
    sixFourCGASeqFreq[[i]][[j]] = fread(generateFilePath(
      directory = generalReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
      cellType = cellType, lesion = "6-4", repitition = names(sixFourCGASeqFreq)[i],
      timepoint = names(sixFourCGASeqFreq[[i]])[j], sequence = "CGA"
    ))
  }
}
```

@@

```{r 6-4_sequence_frequencies, fig.width = 11, fig.height = 10}
plotSequenceFrequencies(sixFourTGGSeqFreq$rep1,
                        title = "6-4 TGG Frequencies Rep1", expansionOffset = expansionOffset,
                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
                        querySequences = c("TGG"))
plotSequenceFrequencies(sixFourTGGSeqFreq$rep2,
                        title = "6-4 TGG Frequencies Rep2", expansionOffset = expansionOffset,
                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
                        querySequences = c("TGG"))

plotSequenceFrequencies(sixFourCGASeqFreq$rep1,
                        title = "6-4 CGA Frequencies Rep1", expansionOffset = expansionOffset,
                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
                        querySequences = c("CGA"))
plotSequenceFrequencies(sixFourCGASeqFreq$rep2,
                        title = "6-4 CGA Frequencies Rep2", expansionOffset = expansionOffset,
                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
                        querySequences = c("CGA"))
```

@@

```{r 6-4_read_length_frequencies}
readAndPlotReadLengthFrequencies("6-4", "rep1", sixFourTimepoints)
readAndPlotReadLengthFrequencies("6-4", "rep2", sixFourTimepoints)
```

>>>>

---
title: "Dm General Read Sequence Figure Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
---

@@

CPDCGASeqFreq = list(rep1 = CPDTimepoints, rep2 = CPDTimepoints)
for (i in seq_along(CPDCGASeqFreq)) {
  for (j in seq_along(CPDCGASeqFreq[[i]])) {
    CPDCGASeqFreq[[i]][[j]] = fread(generateFilePath(
      directory = generalReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
      cellType = cellType, lesion = "CPD", repitition = names(CPDCGASeqFreq)[i],
      timepoint = names(CPDCGASeqFreq[[i]])[j], sequence = "CGA"
    ))
  }
}
```

@@

@@
